---
title: "linear model from Web"
author: "Adriana Pimentel"
date: "Fall 2021"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot
```{r}
plot(SIMS~ARM,data=data)
```
  
The plot shows a positive linear correlation. The standard deviation is around 1.    


### Numerical results
```{r}
cor(SIMS~ARM,data=data)
```
The correlation shown is about .7.

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
The equation of the line is SIMS = .054563*ARM-4.095160.



#### Predict at target point

```{r}
mydata= data.frame(GRIP=94,ARM=88)
```

```{r}
predict(model.1,mydata,interval="prediction")
```

#### scatterplot with model fit
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
``` 

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 

## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
plot(SIMS~GRIP,data=data)
```
  
In this scatterplot there is a positive linear correlation.     

### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```
  
Here the correlation of SIMS and GRIP is .6398 which is a bit smaller than the correlation of SIMS and ARM which was .683.  

### Inferential  (Build model.2)
 
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
``` 
SIMS = .045463*GRIP-4.809675

#### predict model.2 at target point

```{r}
predict(model.2,mydata,interval="prediction")
```
  
Here when GRIP is 94 the prediction of SIMS is -.0536.
  
#### now add the model fit to our plot for model.2
  
```{r}
basicNT <- ggplot(data,aes(y=SIMS,x=GRIP))
``` 

```{r}
basicNT + geom_point() + geom_smooth(method=lm)
``` 


## Model 3 SIM~ARM+GRIP

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
``` 
  
SIMS =ARM **.037311 + .024470**GRIP-5.433871
  
### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```
  
The correlation between SIMS~ARM+GRIP is the highest between the other two models above.  
  
### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
``` 
  
SIMS = .037311(ARM) + .024470(GRIP)-5.433871
  
#### predict model.3 at target point
 
```{r}
predict(model.3,mydata,interval="prediction")
``` 
  
When ARM is 88 and GRIP is 94 together, the prediction of SIMS is 0.149.   

## Comparing nested models ANOVA Test

### Model.1 vs Model.3

```{r}
anova(model.1,model.3)
```
  
The output shows that in model 1 the amount of errors in the mean model is 217.88 but when we include ARM + GRIP, the error in the mean model decreased to 188.43. So, the model with two regressions in it is superior to the model with just one.   
  
### Model.2 vs Model.3

```{r}
anova(model.2,model.3)
```
  
Here model 1 is shown to be better than model 2 as it shows that the error in the GRIP model is 243.07.

## Informally compare Model.1 with model.2

```{r}
anova(model.1,model.2)
```

